Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-02 manuscript/manuscript.Rmd
a word

Note that these measures do not provide information regarding the directional
sensitivity of the predictors on the response. Also, when there are correlated
variables, one should be careful about interpretation, as the result may be
biased by unrealistic records in the permuted dataset. Another ramification
of a group correlated variables is that their inclusion may cause each to
appear less important than if only one is included in the model.

>>>>

Note that these measures do not provide information regarding the directional
sensitivity of the predictors on the response. Also, when there are correlated
variables, one should be careful about interpretation, as the result may be
biased by unrealistic records in the permuted dataset. Another ramification
of a group of correlated variables is that their inclusion may cause each to
appear less important than if only one is included in the model.
